Paper round 2

### 2018-11-30 paper_round2.Rmd
changes

---
title: "Paper"
author: "Ainhoa Magrach"
date: "6 November 2018"
output: html_document
bibliography: library.bib
---

@@

library(bbmle)
AICtab(m1.seed, m2.seed, m3.seed) #best model is m2

@@

library(bbmle)
AICtab(m1.seedb, m2.seedb, m3.seedb) #best model is m2

@@

library(bbmle)
AICtab(m1.seedw, m2.seedw, m3.seedw) #best model is m2

@@

library(bbmle)
AICtab(m1.fruitw, m2.fruitw, m3.fruitw) #best model is m2

@@

library(bbmle)
AICtab(m1.fr, m2.fr, m3.fr) #best model is m2

@@

library(bbmle)
AICtab(m1.seedcomm, m2.seedcomm, m3.seedcomm) #best model is m2

@@

library(bbmle)
AICtab(m1.fwcomm, m2.fwcomm, m3.fwcomm) #best model is m2

@@

library(bbmle)
AICtab(m1.swcomm, m2.swcomm, m3.swcomm) #best model is m2

>>>>

---
title: "Paper round 2"
author: "Ainhoa Magrach"
date: "6 November 2018"
output: html_document
bibliography: library.bib
---

@@

library(bbmle)
AICtab(m1.seed, m2.seed, m3.seed)

@@

library(bbmle)
AICtab(m1.seedb, m2.seedb, m3.seedb)

@@

library(bbmle)
AICtab(m1.seedw, m2.seedw, m3.seedw)

@@

library(bbmle)
AICtab(m1.fruitw, m2.fruitw, m3.fruitw)

@@

library(bbmle)
AICtab(m1.fr, m2.fr, m3.fr)

@@

library(bbmle)
AICtab(m1.seedcomm, m2.seedcomm, m3.seedcomm)

@@

library(bbmle)
AICtab(m1.fwcomm, m2.fwcomm, m3.fwcomm)

@@

library(bbmle)
AICtab(m1.swcomm, m2.swcomm, m3.swcomm)
